%%
%% Author: Arman Ajabkhani (arm.khani@gmail.com)
%% 12/30/2017 AD
%%

\begin{jrsection}{Work Experience}
    \jexperience{
    \jrcaption{Snapp (Smart Transportation System)}
    }{
    \jrsubcaption{Senior Software Engineer}
    }{
    \jrsubsubcaption{July 2019 - Present}
    }{
    \begin{jrdescription}
    {
            - Designing and Developing new generation of Financial micro-services.\linebreak
            - Migrating Finincial Services to Microservices from Monolithic(PHP).\linebreak
            - Providing services with high volumes of concurrent transactions(Java \& Golang).\linebreak
            - Developing services with SpringBoot, Spring Cloud, MySql, Docker and Redis.\linebreak
            - Implementing CI/CD using Gitlab and OpenShift.\linebreak
    }
    \end{jrdescription}
    }
    \jexperience{
        \jrcaption{Sava Arman Kish (Crypto-Currency Exchange)}
    }{
        \jrsubcaption{Senior Java Developer}
    }{
        \jrsubsubcaption{Nov 2018 - Jul 2019}
    }{
        \begin{jrdescription}
        {
        - Monitoring all phases of development process and analysis, design, testing, and implementation \linebreak
        - Developing reactive services using Java, Spring, OpenApi, RxJava and Vert.x and Swagger.\linebreak
        - Designing, development and maintaining Exchange and Notification micro-services. \linebreak
        }
        \end{jrdescription}
    }
    \jexperience{
        \jrcaption{TOSAN (Financial and Payment Solution)}
    }{
        \jrsubcaption{Senior Software Engineer / Team Lead }
    }{
        \jrsubsubcaption{Nov 2011 \textendash Nov 2018}
    }
    {
        \begin{jrdescription}
        {
        \textbf {\textit {Java developer in Channel Manager Team :}}\linebreak
            - Developing functionalities for tracking and authentication and authorization module.\linebreak
            - Developing and Maintaining Exchange and Corporate Banking subsystems.\linebreak
            - Make technical design decisions on exchange subsystem with little supervision.\linebreak
            - Developing and implementing RMI and Web Services (REST / SOAP).\linebreak
            - Works on improvements in development toolset including testing frameworks,\\
        deployment scripts and monitoring libraries.\linebreak
        \textbf {\textit {Team lead in Channel Manager team :}}\linebreak
            - Mentoring, coaching, training, and planning tasks for technical team members.\linebreak
            - Analysis, Design, Development, Deployment \& Maintenance several applications \& micro-services.\linebreak
            - Ensuring code quality and following best software development practices Unit Tests, Code Reviews.\linebreak
        }
        \end{jrdescription}
    }
    \jexperience{
        \jrcaption{Elm o Sanat (Time Attendance System)}
    }{
        \jrsubcaption{C\#/ASP.NET Developer}
    }{
        \jrsubsubcaption{Sep 2010 \textendash Oct 2011}
    }{
        \begin{jrdescription}
        {
        \textbf {\textit {C\#/ASP.NET developer in School product Team:}}\linebreak
            - Implementing several new features and maintain the School application.\linebreak
            - Designing and Developing a customized report generator.\linebreak
            - Implementing a replication using SQL Server and SOAP web service.\linebreak
        }
        \end{jrdescription}
    }
%    \jexperience{
%        \jrcaption{Netbina (Online advertising solution provider)}
%    }{
%        \jrsubcaption{Junior C\#/ASP.NET Developer}
%    }{
%        \jrsubsubcaption{Oct 2006 \textendash Mar 2009}
%    }{
%        \begin{jrdescription}
%        {
%            - Implementing several functionalities for the advertising products.\linebreak
%            - Developing a several feature in Blog Service with C\# and ASP.NET.\linebreak
%        }
%        \end{jrdescription}
%    }
\end{jrsection}
